%-------------------------
% Resume in Latex
% Author : Carlos Salinas
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% Variables
\def\auth{Carlos Salinas}

\documentclass[11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}

% Improved hypertexting
\usepackage{hyperref}
\usepackage{datetime2}
\def\verno{\DTMDate\today}
\hypersetup{colorlinks=true,
  urlcolor=Cerulean,
  pdftitle={\auth - Resume v.\verno},pdfauthor={\auth}}

% \usepackage{lmodern}
\usepackage[default,lining]{FiraSans}
\usepackage[lining,scaled=.95]{FiraMono}
\usepackage[T1]{fontenc}

\usepackage[activate={true,nocompatibility},final,tracking=true,
kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\bf\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\definecolor{Cerulean}{rgb}{0.0, 0.18, 0.39}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge\scshape Carlos Salinas} \\\vspace{10pt}
  Mobile: \href{tel:+17653379606}{(765) 337-9606}\hfill
  GitHub: \href{https://github.com/cdrlos}{\texttt{cdrlos}}\\
  Email: \href{mailto:cemiliosal@gmail.com}{\texttt{cemiliosal@gmail.com}}
 \hfill
 Linkedin: \href{https://www.linkedin.com/in/carlos-salinas-64588b160/}{\texttt{carlos-salinas-64588b160}}
\end{center}

% \section{Objective}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University, West Lafayette, IN}{Aug.\ 2020}
      {Master of Science in Mathematics}{GPA: 3.73/4.0}
    \resumeSubheading
      {University of Texas--Pan American, Edinburg, TX}{May 2014}
      {Bachelor of Science in Mathematics}{GPA: 3.86/4.0}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, Julia, C++, R, Java, SQL, Matlab} \\
     \textbf{Developer Tools}{: Git, Emacs, Vim, GCC, Valgrind, Gradle} \\
     \textbf{Other Software}{: Linux, LaTeX, Mathematica, Markdown, Jekyll, Bash, Awk}\\
     \textbf{Natural Languages}{: English---native, Spanish---native, Russian---fluent, Persian---conversant, French---proficient}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Department of Mathematics, Purdue University}{West Lafayette, IN}
      {Research Assistant/Teaching Assistant}{Aug.\ 2014 -- May 2020}
      \resumeItemListStart
      \resumeItem{Led recitation sections for undergraduate math courses, including Calculus 1, 2, 3, Differential Equations, and Linear Algebra. Graded homework, wrote quizzes, and proofread exams.}
      \resumeItem{Hosted a \href{https://www.math.purdue.edu/~salinac}{website} to post math related content for students, such as notes, links to university resources, course related deadlines, practice problems, quiz solutions, and class quiz and midterm statistics.}
      \resumeItem{Studied finite quotients of triangle groups and nilpotent groups. Wrote a program in GAP to compute finite quotients to distinguish inequivalent triangle groups following a result by Bridson--Conder--Reid that triangle groups are profinitely rigid.}
      \resumeItemListEnd
    \resumeSubheading
      {School of Mathematical and Statistical Sciences, University of Texas--Pan American}{Edinburg, TX}
      {Undergraduate Research Assistant/System Administrator}{Sep.\ 2013 -- May 2014}
      \resumeItemListStart
        \resumeItem{Managed the Experimental Algebra and Geometry Lab's Fedora cluster. Administered users and user permissions, updated software, and configured the lab's Nvidia GPU for usage in simulations requiring parallelization.}
        \resumeItem{Wrote an program to compute 2-special word families up to word-length 30 using trace formulas to significantly reduce the search space. Published the sequence of such words on the On-line Encyclopedia of Integer Sequences \href{https://oeis.org/A237623}{A237623}. Presented the result at the Character Varieties and Geometry Structures Workshop held at Howard University.}
        \resumeItemListEnd
     \resumeSubheading
      {Department of Materials Science and Engineering, Massachusetts Institute of Technology }{Cambridge, MA}
      {Undergraduate Research Assistant}{Jun.\ 2010 -- Aug.\ 2010}
      \resumeItemListStart
        \resumeItem{Tested heat-treated Ti-Ta alloys of varying compositions for shape-memory and superelastic properties by means of hot oil recovery test. Took metallographs of samples to study the microstructure. Performed of mechanical tests, such as tensile test, and fatigue tests, and recorded the results.}
      \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
\resumeSubHeadingListEnd

% -----------LEADERSHIP/OUTREACH---------
  \section{Outreach Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {College of Agriculture, Purdue University}{West Lafayette, IN}
      {Academic Boot Camp for Purdue's Minority Engineering Program}{Jun.\ 2018 -- Aug.\ 2018}
      \resumeItemListStart
      \resumeItem{Simulated a first semester Calculus experience for incoming undergraduate students in the MEP. Prepared and graded student homework and midterms. Assigned final letter grades and gave course recommendations.}
      \resumeItemListEnd
      \resumeSubheading
      {School of Mathematical and Statistical Sciences, University of Texas--Pan American}{Edinburg, TX}
      {Outreach Assistant for the Experimental Algebra \& Geometry Lab}{Sep. 2012 -- May 2014}
      \resumeItemListStart
      \resumeItem{Introduced K12 students to higher level mathematics such as modular arithmetic, complex numbers, and spherical geometry through kinesthetic activities. Introduced senior members of the community to hyperbolic crocheting and non-Euclidean geometry.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXPOSITION-----------
% \section{Presentations}
%     \resumeSubHeadingListStart
%     \resumeSubheading
%     {Superpositions of a Sigmoidal Function}{Feb.\ 6, 2019}{Machine Learning Reading Group, Purdue University}{}
%     \resumeItemListStart
%     \resumeItem{Presented with a partner a foundational result in Universal Approximation Theory to an audience of approx.\ 40.}
%     \resumeItem{Introduced the results and language necessary to prove that sigmoids can approximate any continuous function.}
%     \resumeItem{Proved that ReLUs are \emph{discriminatory}, as an application, and therefore universal approximators.}
%     \resumeItemListEnd
    % \resumeSubheading
    % {Observations}{June 2020}{\href{https://ravat1.github.io/2020DSB-website/}{Data Science Bootcamp} at University of Chicago at Urbana-Champaign}{}
    % \resumeItemListStart
    % \resumeItem{Wrote an RMarkdown notebook to analyze book ratings on a subset of GoodReads' database.}
    % \resumeItem{Performed linear regression to model the popularity of prolific authors.}
    % \resumeItem{Performed ANOVA on the data to get an overview of the different features of the data and how they relate to the \emph{popularity} of a given author.}
    % \resumeItemListEnd
    % \resumeSubHeadingListEnd

%-----------PROJECTS-----------
% \section{Projects}
% \resumeSubHeadingListStart
% \resumeSubHeadingListEnd

% -------------------------------------------
\end{document}
