% Cover letter using letter.cls
\documentclass[12pt]{letter} % default is 10 pt
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
<<<<<<< HEAD
\def\verno{Coca-Cola Southwest Beverages QA Tech (62265)}
=======
\usepackage{datetime2}
\def\verno{IDEA SIS Integration and Data Analytics\DTMDate\today}
>>>>>>> 62304bb5a7169b41ec30daf4a405bad334f0118d
% \def\verno{PNNL Job ID: 311747 \DTMDate\today}
\hypersetup{colorlinks=true,
urlcolor=Blue,
pdftitle={Cover Letter \verno},
pdfauthor={Carlos Salinas}}

% Font
<<<<<<< HEAD
% \usepackage[default]{roboto}
% \usepackage[scaled=.98]{roboto-mono}
\usepackage[default]{sourcesanspro}
\usepackage[scaled=.98]{sourcecodepro}
% \usepackage[default,lining]{FiraSans}
% \usepackage[scaled=.98,lining]{FiraMono}
=======
% \usepackage[default,osf]{sourcesanspro}
% \usepackage[scaled=.98]{sourcecodepro}
\usepackage[default]{roboto}
\usepackage[scaled=.98]{roboto-mono}
% \usepackage[default]{FiraSans}
% \usepackage[scaled=.98]{FiraMono}
% \usepackage{lmodern}
% \renewcommand{\familydefault}{\sfdefault}
>>>>>>> 62304bb5a7169b41ec30daf4a405bad334f0118d
\usepackage[T1]{fontenc}

\input{glyphtounicode}
\pdfgentounicode=1

% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
% \newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document}

\address{
Carlos Salinas \\
7507 Camelot Dr\\
Mission, TX 78572\\
{\href{tel:+17653379606}{(765) 337-9606}}\\[-15pt]}

\begin{letter}{
<<<<<<< HEAD
Coca-Cola Southwest Beverages\\
2400 W Expy 83\\
McAllen, TX 78501
=======
    IDEA Headquarters Rio Grande Valley\\
    2115 W Pike Blvd,\\
    Weslaco, TX 78596
    % Pacific Northwest National Laboratory\\
    % 902 Battelle Blvd,\\
    % Richland, WA 99354
>>>>>>> 62304bb5a7169b41ec30daf4a405bad334f0118d
}

\vfill % forces letterhead to top of page

<<<<<<< HEAD
\opening{Dear Hiring Manager at XPO Logistics' McAllen branch,}

I writing to you because I am interested in the position of warehouse associate at your McAllen location. I have experience working freight and receiving both at the Home Depot and the H-E-B. As part of those jobs I often operated machinery to stock and place bulk product in its appropriate location making sure to mark the amount and exact location with my RF device if need. I am very communicative, highly attentive, I do not make mistakes and I make sure to let my supervisor know about any problems that may arise in the work place. I have the ability to adjust my routine to my schedule so I can work any shift of the day. I have exceedingly good math skills and computer skills. You do not want to miss out on this potential employee.

I hope to hear from you soon.
=======
\opening{Dear Hiring Manager at IDEA Public Schools,}

% I'm writing to you to express my interest in the Early Career Data Scientist position (Job ID 311747).
I am writing to you to express my interest in the SIS Integration and Data Analyst position.

I am a firm believer that education is THE BEST WAY to serve underrepresented communities.
Despite the significant \href{https://www.usnews.com/education/best-colleges/paying-for-college/articles/2017-09-20/see-20-years-of-tuition-growth-at-national-universities}{rise in tuition} in recent years, there are no shortage of studies showing that a college degree is still a worthwhile investment for most people (see \href{https://www.cnn.com/2019/06/06/success/college-worth-it}{here} and \href{https://libertystreeteconomics.newyorkfed.org/2019/06/despite-rising-costs-college-is-still-a-good-investment.html}{here}).
It is, therefore, of upmost importance that we prepare our high school graduates to be successful in college.

I am committed to the mission of IDEA Public Schools and prepared to engage in the problems you face to the best of my capacity.
As a recent graduate from Purdue University's graduate program in mathematics, I am more than well equipped to tackle the sorts of logic problems one encounters in making SQL queries.
I, moreover, have an excellent understanding of PostgreSQL databases and how they integrate with other applications (primarily JDBC, but also psycopg2) and data analysis and artificial intelligence experience from my studies.

I am confident that I can provide a lot of value to your organization.
>>>>>>> 62304bb5a7169b41ec30daf4a405bad334f0118d

\closing{Sincerely,\\[5pt]
Carlos Salinas}
\end{letter}
\end{document}
