%-------------------------
% Resume in Latex

% Author : Carlos Salinas
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% Variables
\def\auth{Carlos Salinas}

\documentclass[12pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{verbatim}

% Improved hypertexting
\usepackage{hyperref}
\def\verno{2.0.2}
\hypersetup{colorlinks=true,
urlcolor=Blue,
pdftitle={\auth - Resume v.\verno},
pdfauthor={\auth}}

% Font
% \usepackage[default]{roboto}
% \usepackage[scaled=.98]{roboto-mono}
\usepackage[default]{sourcesanspro}
\usepackage[scaled=.98]{sourcecodepro}
% \usepackage[default,lining]{FiraSans}
% \usepackage[scaled=.98,lining]{FiraMono}
\usepackage[T1]{fontenc}

\usepackage[activate={true,nocompatibility},final,tracking=true,
kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}

\input{glyphtounicode}
\pdfgentounicode=1

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\bf\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\definecolor{Cerulean}{rgb}{0.0, 0.18, 0.39}
\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\cheat[1]{\makebox[0pt][l]{\pdfliteral page {q 3 Tr} #1 \pdfliteral page {Q}}}

%%%%%% RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%
\begin{document}
% ----------CHEAT CODE-----------------------------
\cheat{Operates forklift following Company standards and guidelines by safely picking up, moving, placing, and positioning merchandise pallets. Receives, stocks, and organizes merchandise and supplies from distribution centers and suppliers throughout the facility by managing inventory flow; following company policy and procedures for utilizing equipment appropriately; merchandising; working inventory exceptions; correcting shelf capacities; and completing and retaining required paperwork, logs, and other documentation. Provides member service by acknowledging the member and identifying member needs; providing guidance and support to members regarding self- service technology; assisting members with purchasing decisions; locating merchandise; resolving member issues and concerns; and promoting the company's products and services. Maintains safety of facility according to company policies and procedures by conducting safety sweeps; following forklift spotting procedures; following procedures for handling and disposing of hazardous materials; following company steel standard guidelines; and correcting and reporting unsafe situations to management. Maintains the sales floor and merchandising presentation in accordance with company policies and procedures by properly zoning the area; stocking and rotating merchandise; removing damaged or out-of-date goods; setting up, cleaning, and organizing product displays; maintaining modular integrity; receiving, sorting, staging, and delivering merchandise; ensuring prominent display of promotional and seasonal merchandise; processing defective merchandise; following company and regulatory policies and procedures for sanitation and food safety; and monitoring the area of shrink, security risks, and safety. Ensures club pick up orders are filled by assisting with picking club pick up orders throughout the day and staging; ensuring products are selected and staged according to company policy and procedures; ensuring Merchandising Associates pick orders within acceptable timeframe and are staged properly; and performing occasional audits for accuracy. Complies with company policies, procedures, and standards of ethics and integrity by implementing related action plans; using the Open Door Policy; and applying these in executing business processes and practices. Completes work assignments and priorities by using policies, data, and resources; collaborating with managers, co-workers, customers, and other business partners; identifying priorities, deadlines, and expectations; carrying out tasks; communicating progress and information; determining and recommending ways to address improvement opportunities; and adapting to and learning from change, difficulties, and feedback. Minimum Qualifications... Outlined below are the required minimum qualifications for this position. If none are listed, there are no minimum qualifications. Minimum Qualifications90 days of prior experience with Forklift Certification. Ability to safely utilize pallet jacks. Must be 18 years of age or older Preferred Qualifications... Outlined below are the optional preferred qualifications for this position. If none are listed, there are no preferred qualifications. Customer Service, Retail Experience, Supervising a team}

%----------HEADING--------------------------------
\begin{center}
  \textbf{\Huge\scshape Carlos Salinas} \\\vspace{10pt}
\end{center}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{0.65in} \= \hspace{1.15in} \= \kill % Spacing within the block
  \small \textbf{Phone:} \> \small\href{tel:+17653379606}{(765) 337-9606}\\
  \small \textbf{Email:} \> \small\href{mailto:cemiliosal@gmail.com}{\texttt{cemiliosal@gmail.com}}
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{0.65in} \= \hspace{1.15in} \= \kill % Spacing within the block
  \small \textbf{GitHub:} \> \small \href{https://github.com/cdrlos}{\texttt{cdrlos}}\\
  \small \textbf{Linkedin:} \> \small \href{https://www.linkedin.com/in/carlos-salinas-64588b160/}{\texttt{carlos-salinas-64588b160}}
\end{tabbing}}

%-----------PROGRAMMING SKILLS--------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
      \textbf{Programming Languages}{: Python, Ruby, R, JavaScript, Java}\\
      \textbf{Developer Tools}{: Emacs, (Neo)vim, Git, Ruby on Rails, PostgreSQL, Node.js, Jupyter} \\
      \textbf{Other Software}{: Linux, Bash, LaTeX, Markdown, Excel (Google Sheets) proficiency}\\
      \textbf{Natural Languages}{: English---native, Spanish---native, Russian---fluent}\\
      \textbf{Misc.\ Skills}{: Touch-typing (187 WPM), customer service, fort lift, order picker, power and hand tool, basic auto mechanics, basic assembly, heavy lifting}
  }}
 \end{itemize}

 %-----------EXPERIENCE---------------------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{TELUS International}{Remote}
{Map Analyst}{Jan. 2021 -- present}
\resumeItemListStart
\resumeItem{Determine relevance and accuracy of map search results as part of an AI app pipeline.}
\resumeItem{Determine accuracy of business information such as address, unit number, phone number, hours of operation and current operation status doing online research.}
\resumeItemListEnd

\resumeSubheading
{The Home Depot}{Lafayette, IN}
{Seasonal Garden Associate}{Mar. 2021 -- Jun. 2021}
\resumeItemListStart
\resumeItem{Engage customers using the GET method. Provide product information and availability.}
\resumeItem{Pack down the shelves and displays if possible. Assess product availability using company RF scanner.}
\resumeItem{Operate fork lift or order picker outside store to load large customer orders, unload shipments for outside garden product, and to bring down or put up product in the overhead.}
\resumeItemListEnd

\resumeSubheading
{Purdue University}{West Lafayette, IN}
{Research Assistant/Teaching Assistant}{Aug.\ 2014 -- Aug. 2020}
\resumeItemListStart
\resumeItem{Led recitation for undergraduate math courses, including Calculus 1, 2, 3, Differential Equations and Linear Algebra.}
\resumeItem{Published course-related content for students, such as lesson notes, quizzes, quiz, and midterm solutions, and score statistics to a university-hosted website.}
\resumeItem{As a researcher, wrote notebooks to study the finite quotients of triangle and the free nilpotent group.}
\resumeItemListEnd

\resumeSubheading
{University of Texas--Pan American}{Edinburg, TX}
{Undergraduate Research Assistant/System Administrator}{Sep.\ 2013 -- May 2014}
\resumeItemListStart
\resumeItem{Managed the Experimental Algebra and Geometry Lab's Linux cluster, which included administering users, installing software, running services, and configuring the lab's GPU for use with Mathematica's CUDALink.}
\resumeItem{Wrote an program to compute 2-special word families up to word-length 30 which leveraged the existence of trace formulas and dependence on lower order polynomials to reduce the search space. Published the sequence on the On-line Encyclopedia of Integer Sequences \href{https://oeis.org/A237623}{A237623}.}
\resumeItemListEnd

\resumeSubheading
{H-E-B}{Pharr, TX}
{Overnight Stocker}{Sep.\ 2011 -- Dec 2011}
\resumeItemListStart
\resumeItem{Walk designated aisles and start recovery, i.e.\ ensure merchandise is well stocked, in its proper place, and presentable; ensure shelves and displays maintain a clean, presentable looks.}
\resumeItem{Discuss nightly goals and tasks with stock controller.}
\resumeItem{Spot depleting product in the aisles and replenish products onto shelves.}
resumeItem{Load and unload bulk product with the assistance of a pallet jack if necessary.}
\resumeItemListEnd

\resumeSubheading
{Massachusetts Institute of Technology }{Cambridge, MA}
{Undergraduate Research Assistant}{Jun.\ 2010 -- Aug.\ 2010}
\resumeItemListStart
\resumeItem{Tested heat-treated Ti-Ta alloys of varying compositions for shape-memory and superelastic properties by means of hot oil recovery test. Took metallographs of samples to study the microstructure. Performed of mechanical tests, such as tensile test, and fatigue tests, and recorded the results.}
\resumeItemListEnd

% \resumeSubheading
% {De Maiz Tortilleria}{Pharr, TX}
% {Cashier}{Aug.\ 2010 -- Dec.\ 2010}
% \resumeItemListStart
% \resumeItem{Work the register. Collected payment from customers. Maintained the store tidy and restocked merchandise.}
% \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Purdue University, West Lafayette, IN}{Aug.\ 2020}
{MS in Mathematics}{GPA: 3.73/4.0}
\vspace{-15pt}
\resumeSubheading
{University of Texas-Pan American, Edinburg, TX}{May 2014}
{BS in Mathematics}{GPA: 3.86/4.0}
\resumeSubHeadingListEnd

 % -----------Multiple Positions Heading-----------
 %    \resumeSubSubheading
 %     {Software Engineer I}{Oct 2014 - Sep 2016}
 %     \resumeItemListStart
 %        \resumeItem{Apache Beam}
 %          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
 %     \resumeItemListEnd
 %    \resumeSubHeadingListEnd
 %-------------------------------------------
 \resumeSubHeadingListEnd

 % -----------LEADERSHIP/OUTREACH---------
 \section{Outreach Experience}
 \resumeSubHeadingListStart
 \resumeSubheading
 {Purdue University}{West Lafayette, IN}
 {Academic Boot Camp for Purdue's Minority Engineering Program}{Jun.\ 2018 --
 Aug.\ 2018}
 \resumeItemListStart
 \resumeItem{Simulated a first semester Calculus experience for incoming
 undergraduate students in the MEP. Prepared and graded student homework and
 midterms. Assigned final letter grades and gave course recommendations based on student perfromance.}
 \resumeItemListEnd
 \resumeSubheading
 {University of Texas--Pan American}{Edinburg, TX}
 {Outreach Assistant for the Experimental Algebra \& Geometry Lab}{Sep. 2012 -- May 2014}
 \resumeItemListStart
 \resumeItem{Introduced K12 students to interesting topics in higher mathematics,
 such as modular arithmetic, complex numbers, and spherical and hyperbolic geometry through kinesthetic activities.}
 \resumeItemListEnd
 \resumeSubHeadingListEnd

% \section{Projects}
% \resumeSubHeadingListStart
% \resumeSubItem{\href{https://www.math.purdue.edu/~salinac}{math.purdue.edu/{\textasciitilde}salinac}}{University home page.}
% \resumeSubHeadingListEnd

 %-----------EXPOSITION-----------
 % \section{Presentations}
 %     \resumeSubHeadingListStart
 %     \resumeSubheading
 %     {Superpositions of a Sigmoidal Function}{Feb.\ 6, 2019}{Machine Learning Reading Group, Purdue University}{}
 %     \resumeItemListStart
 %     \resumeItem{Presented with a partner a foundational result in Universal Approximation Theory to an audience of approx.\ 40.}
 %     \resumeItem{Introduced the results and language necessary to prove that sigmoids can approximate any continuous function.}
 %     \resumeItem{Proved that ReLUs are \emph{discriminatory}, as an application, and therefore universal approximators.}
 %     \resumeItemListEnd
 % \resumeSubheading
 % {Observations}{June 2020}{\href{https://ravat1.github.io/2020DSB-website/}{Data Science Bootcamp} at University of Chicago at Urbana-Champaign}{}
 % \resumeItemListStart
 % \resumeItem{Wrote an RMarkdown notebook to analyze book ratings on a subset of GoodReads' database.}
 % \resumeItem{Performed linear regression to model the popularity of prolific authors.}
 % \resumeItem{Performed ANOVA on the data to get an overview of the different features of the data and how they relate to the \emph{popularity} of a given author.}
 % \resumeItemListEnd
 % \resumeSubHeadingListEnd
 % -------------------------------------------
 \end{document}
